---
title: "SC_together.Rmd"
author: "Nick_Panyushev"
date: "4/17/2021"
output: html_document
---

```{r setup, include=FALSE}
#BiocManager::install(c('multtest', "DropletUtils"), Ncpus = 7)
#BiocManager::install("MAST", Ncpus = 7)
#install.packages("irlba")
#install.packages("scico")
#install.packages("Seurat")
#install.packages("DropletUtils")
#install.packages("tidyverse")
#install.packages("ggpointdensity")
#install.packages("scales")
#install.packages("hexbin")

setwd("~/Urchin_projects/Spur_single-cell/")
library(hexbin)
library(stringr)
library(Matrix)
library(irlba)
library(scico)
library(Seurat)
library(DropletUtils)
library(tidyverse)
library(ggpointdensity)
library(scales)
library(MAST)
theme_set(theme_bw())
source("SC_functions.R")
```


```{r SCTransform}
if (!file.exists("Seurat_tranformed.RData")){
  seu_64 <- SCTransform(seu_64, conserve.memory = T, verbose = TRUE)
seu_morula <- SCTransform(seu_morula, conserve.memory = T, verbose = TRUE)
seu_early_blastula <- SCTransform(seu_early_blastula, conserve.memory = T, verbose = TRUE)
gc()
seu_hatched_blastula_1 <- SCTransform(seu_hatched_blastula_1, conserve.memory = T, verbose = TRUE)
gc()
seu_hatched_blastula_2 <- SCTransform(seu_hatched_blastula_2, conserve.memory = T, verbose = TRUE)
gc()
seu_early_gastrula_1 <- SCTransform(seu_early_gastrula_1, conserve.memory = T, verbose = TRUE)
gc()
seu_early_gastrula_2 <- SCTransform(seu_early_gastrula_2, conserve.memory = T, verbose = TRUE)

seu_mesenchyme_blastula_1 <- SCTransform(seu_mesenchyme_blastula_1, conserve.memory = T, verbose = TRUE)
gc()
seu_mesenchyme_blastula_2 <- SCTransform(seu_mesenchyme_blastula_2, conserve.memory = T, verbose = TRUE)
gc()
seu_late_gastrula_1 <- SCTransform(seu_late_gastrula_1, conserve.memory = T, verbose = TRUE)
gc()
seu_late_gastrula_2 <- SCTransform(seu_late_gastrula_2, conserve.memory = T, verbose = TRUE)
gc()

save(seu_64, seu_morula,
     seu_early_blastula,
     seu_hatched_blastula_1, seu_hatched_blastula_2, 
     seu_mesenchyme_blastula_1, seu_mesenchyme_blastula_2, 
     seu_early_gastrula_1, seu_early_gastrula_2, 
     seu_late_gastrula_1, seu_late_gastrula_2,
     file = "Seurat_tranformed.RData")
}else{
  load("Seurat_tranformed.RData")
}
```

```{r set stages}
seu_64$stage <- "64_cells"
seu_morula$stage <- "morula"
seu_early_blastula$stage <- "early_blastula"
seu_hatched_blastula_1$stage <- "hatched_blastula"
seu_hatched_blastula_2$stage <- "hatched_blastula"
seu_early_gastrula_1$stage <- "early_gastrula"
seu_early_gastrula_2$stage <- "early_gastrula"
seu_mesenchyme_blastula_1$stage <- "mesenchyme_blastula"
seu_mesenchyme_blastula_2$stage <- "mesenchyme_blastula"
seu_late_gastrula_1$stage <- "late_gastrula"
seu_late_gastrula_2$stage <- "late_gastrula"
```

```{r joining datasets}
if(!file.exists("seurat_all.Rdata")){
  obj.list <- list(seu_64,
                 seu_morula,
                 seu_early_blastula,
                 seu_hatched_blastula_1,
                 seu_hatched_blastula_2,
                 seu_mesenchyme_blastula_1,
                 seu_mesenchyme_blastula_2,
                 seu_early_gastrula_1,
                 seu_early_gastrula_2, 
                 seu_late_gastrula_1,
                 seu_late_gastrula_2) 

  options(future.globals.maxSize= 8589934592)
  features <- SelectIntegrationFeatures(object.list = obj.list, nfeatures = 2000)
  obj.list <- PrepSCTIntegration(object.list = obj.list, anchor.features = features, verbose = FALSE)

  if (!file.exists("anchors.RData")){
    anchors <- FindIntegrationAnchors(object.list = obj.list, normalization.method = "SCT", 
    anchor.features = features, verbose = FALSE)
    save(anchors, file = "anchors.RData")
  }else{
    load("anchors.RData")
  }
  seurat_joined <- IntegrateData(anchorset = anchors, normalization.method = "SCT", 
      verbose = TRUE)
  save(seurat_joined, file = "seurat_all.Rdata")
}else{
  load("seurat_all.Rdata")
}
```

```{r PCA}
seurat_joined <- RunPCA(seurat_joined, verbose = FALSE)
ElbowPlot(seurat_joined, ndims = 80)
seurat_joined <- RunTSNE(seurat_joined, dims=1:20)
DimPlot(seurat_joined, reduction = "tsne") + 
  NoLegend()
```

```{r UMAP}
seurat_joined <- RunUMAP(seurat_joined, dims=1:20)
DimPlot(seurat_joined, reduction = "umap") + NoLegend()
DimPlot(seurat_joined, reduction = "umap", label = TRUE, split.by = "stage")
```

```{r Markers}
seurat_joined <- FindNeighbors(seurat_joined, dims = 1:40, verbose = FALSE)
seurat_joined <- FindClusters(seurat_joined, resolution=0.6, verbose = FALSE)
DimPlot(seurat_joined, reduction = "tsne", label = TRUE, split.by = "stage") + NoLegend()
DimPlot(seurat_joined, reduction = "umap", label = TRUE) + NoLegend()

allMarkers <- FindAllMarkers(seurat_joined, max.cells.per.ident = 100, test.use = "MAST", only.pos = T)
goodMarkers <- allMarkers %>% group_by(cluster) %>% top_n(n = 5, wt = avg_log2FC) %>% pull(gene)
goodMarkers[1:3]

FeaturePlot(seurat_joined, goodMarkers[1:3], cols=c("blue", "red"), reduction="umap", ncol=3)
VlnPlot(seurat_joined, goodMarkers[1:3], pt.size = 0.01)
```

```{r Highly variable genes}
seurat_joined <- FindVariableFeatures(seurat_joined, nfeatures = 3000)
top10_variable <- head(VariableFeatures(seurat_joined), 10)
fp <- FeaturePlot(seurat_joined, top10_variable[9], cols = c("blue", "red"), reduction="umap", ncol=3, interactive = T)
fp
#plot1 <- VariableFeaturePlot(seurat_joined, log = FALSE)
#LabelPoints(plot = plot1, points = top10_variable, repel = TRUE)
#print(tr2g[gene_var %in% top10, info])
save(seurat_joined, file = "Seurat_processed.Rdata")
load("Seurat_processed.Rdata")
top10_variable